Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-22 analysis/paper/paper.Rmd

> Consider graphic of spp frequency of occurrence (maybe some panel-rich figure, one panel per spp, showing annual average percentage of daily observations in which spp was sighted - as line-connected points?- ordered from most frequently observed spp to least frequently. Think about appropriate estimator so annual value accounts for variation in survey effort across years.) likely needs to be a full page figure (e.g., we'll need to set  fig.width and fig.height)

```{r EDA_AllSpp_Frequency, eval=TRUE, cache = FALSE, include = FALSE}
# lets discuss what I'm thinking of. It is of secondary importance, so don't want this 
# to consume tons of your time.

@@

```{r SpeciesTiming, eval=TRUE, cache = FALSE, include = FALSE}
# Madeleine: write a script to extract, for just the target species listed at line 250, 
# just the dates each year that each of the target species was observed (somewhere in the survey areas - don't care which, at the moment)
# then add a layer to the ggplot 'Plot1' (horrid name, by the way) to visually distinguish those dates for that species.
# will have to play around to see if it is feasible to do this by faceting on the species or just make a separate 
# timing graph for each species - your call. It will be unreadable if try and put all of the target species on 
# a single plot

>>>>

> MADELEINE: add a graphic of spp frequency of occurrence (maybe some panel-rich figure, one panel per spp, showing annual average percentage of daily observations in which spp was sighted - as line-connected points?- ordered from most frequently observed spp to least frequently. (e.g., use facets). LET"S DISCUSS - Think about appropriate estimator so annual value accounts for variation in survey effort across years.) likely needs to be a full page figure (e.g., we'll need to set  fig.width and fig.height)

```{r EDA_AllSpp_Frequency, eval=TRUE, cache = FALSE, include = FALSE, fig.height=8, fig.width=6}
# lets discuss what I'm thinking of. It is of secondary importance, so don't want this 
# to consume tons of your time.

@@

```{r SpeciesTiming, eval=TRUE, cache = FALSE, include = FALSE}
# MADELEINE: write a script to extract, for just the target species listed at line 250, 
# just the dates each year that each of the target species was observed (somewhere in the survey areas - don't care which, at the moment)
# then add a layer to the ggplot 'Plot1' (horrid name, by the way) to visually distinguish those dates for that species.
# will have to play around to see if it is feasible to do this by faceting on the species or just make a separate 
# timing graph for each species - your call. It will be unreadable if try and put all of the target species on 
# a single plot
